Comparison of simulation to theory

### 2016-02-09 sims/compare-to-theory.Rmd
adjusted r vals (and saved them out) in run_sims

```{r sim_results}
if (!exists("simchunks.file")) { 
    simchunks.file <- "simulation_SIGMA1_Ninds25000_ndemes50_s0.1_tau100_run2016-01-11_simsums_chunks.Robj" 
}
load(simchunks.file)  # provides 'chunks'
get_simparams <- function (fname) {
    strings <- c( sigma="SIGMA", ninds="Ninds", ndemes="ndemes", s="s", tau="tau" )
    lapply( strings, function (x) { as.numeric(gsub(sprintf(".*[/_]%s([0-9.]+)_.*",x),"\\1",simchunks.file)) } )
}
sim.params <- get_simparams( simchunks.file )
# recombination distances, hard-coded
sim.rvals <- c(0,0.01,0.5)
# spatial locations of the demes
xx <- seq_len(sim.params$ndemes)-(sim.params$ndemes+1)/2
theory.params <- list( sigma=trueSigma(sim.params$sigma), s=sim.params$s, tau=sim.params$tau, 
       density=sim.params$ninds/sim.params$ndemes,
       width=sim.params$ndemes )
simchunks.file
unlist(theory.params)
```

@@

>>>>

```{r sim_results}
if (!exists("simchunks.file")) { 
    simchunks.file <- "simulation_SIGMA1_Ninds25000_ndemes50_s0.1_tau100_run2016-01-11_simsums_chunks.Robj" 
}
load(simchunks.file)  # provides 'chunks' and 'chunks.rvals'
get_simparams <- function (fname) {
    strings <- c( sigma="SIGMA", ninds="Ninds", ndemes="ndemes", s="s", tau="tau" )
    lapply( strings, function (x) { as.numeric(gsub(sprintf(".*[/_]%s([0-9.]+)_.*",x),"\\1",simchunks.file)) } )
}
sim.params <- get_simparams( simchunks.file )
# recombination distances
# sim.rvals <- c(0,0.5-0.01,0.5)
sim.rvals <- sapply( chunks.rvals, "[", 2 )
# spatial locations of the demes
xx <- seq_len(sim.params$ndemes)-(sim.params$ndemes+1)/2
theory.params <- list( sigma=trueSigma(sim.params$sigma), s=sim.params$s, tau=sim.params$tau, 
       density=sim.params$ninds/sim.params$ndemes,
       width=sim.params$ndemes )
simchunks.file
unlist(theory.params)
```

@@

The probability of seeing a haplotype of length at least $\ell$
covering position $r$ on the genome at location $x$ in space: for fixed $\ell$,
against $r$ and/or $x$.

We'll do this against $x$ at a few values of $r$ because that's what we have.
```{r theory_haps, cache=TRUE}
rgrid <- setup.grid.1D(x.up=-0.5, x.down=0.5, N=41)
hap.soln <- forwards_backwards_haplotypes(s=theory.params$s, times=tt, xgrid=xgrid, rgrid=rgrid,
                           sigma=theory.params$sigma, 
                           fwds.grid=fgrid, fwds.soln=fwds.soln )
```
